\documentclass[reqno]{amsart}
\usepackage{amssymb, amsmath}
\usepackage[left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm]{geometry}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,positioning,calc}
\setmonofont{DejaVu Sans Mono}[Scale=MatchLowercase]

% Define colors for code listing
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

% Listings configuration
\lstdefinelanguage{Lean}{
  keywords={def, theorem, lemma, axiom, structure, inductive, where, deriving, noncomputable, opaque, section, namespace, open, end, variable, variables, Prop, Type, Sort, if, then, else, let, in, do, case, match, with, by, intro, exact, apply, rw, simp, rcases, obtain, use, have, calc, contradiction, exfalso, constructor, split_ifs},
  keywordstyle=\color{blue}\bfseries,
  ndkeywords={class, export, boolean, throw, implements, import, this},
  ndkeywordstyle=\color{darkgray}\bfseries,
  identifierstyle=\color{black},
  sensitive=true,
  comment=[l]{--},
  morecomment=[s]{/-}{-/},
  commentstyle=\color{codegreen}\ttfamily,
  stringstyle=\color{red}\ttfamily,
  morestring=[b]"
}

\lstset{
  backgroundcolor=\color{backcolour},
  basicstyle=\ttfamily\footnotesize,
  breakatwhitespace=false,
  breaklines=true,
  captionpos=b,
  keepspaces=true,
  numbers=left,
  numbersep=5pt,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=2,
  extendedchars=true,
  mathescape=true,
  literate={ℂ}{$\mathbb{C}$}1
           {ℝ}{$\mathbb{R}$}1
           {ℕ}{$\mathbb{N}$}1
           {ℤ}{$\mathbb{Z}$}1
           {∀}{$\forall$}1
           {∃}{$\exists$}1
           {→}{$\to$}1
           {↔}{$\leftrightarrow$}1
           {≤}{$\le$}1
           {≥}{$\ge$}1
           {⊆}{$\subseteq$}1
           {⊂}{$\subset$}1
           {∪}{$\cup$}1
           {∩}{$\cap$}1
           {⋃}{$\bigcup$}1
           {⋂}{$\bigcap$}1
           {∈}{$\in$}1
           {∉}{$\notin$}1
           {∅}{$\emptyset$}1
           {⟨}{$\langle$}1
           {⟩}{$\rangle$}1
}

\title{Initial Formalization of the MLC Conjecture for Quadratic Polynomials}
\author{\url{https://github.com/kirill-kondrashov/mlc}}
\date{\today}

\begin{document}

\begin{abstract}
  This document presents an initial formalization of an attempt to prove of the Local Connectivity of the Mandelbrot Set (MLC) for quadratic polynomials, focusing on the reduction to Yoccoz's Theorem. The formalization is implemented in Lean 4. The Lean 4 code was produced by a combination of actions of AI assistant and manual fixes and now is under manual verification, see \url{https://github.com/kirill-kondrashov/mlc/blob/main/README.md} for the latest updates. It can be used as a sandbox to check the ideas that are immediately verified with Lean 4 as a part of a closed loop pipeline.
\end{abstract}

\maketitle

\section{Introduction}

The Mandelbrot set $\mathcal{M}$ is the set of parameters $c \in \mathbb{C}$ for which the orbit of 0 under $f_c(z) = z^2 + c$ is bounded. The MLC conjecture asserts that $\mathcal{M}$ is locally connected. This result implies the density of hyperbolic components (structural stability).

This formalization covers the reduction of the conjecture to the "Shrinking Puzzle Pieces" theorem (Yoccoz's Theorem) for non-renormalizable parameters, and assumes the infinitely renormalizable case as an axiom (following Lyubich).

\section{The Open Problem}

The MLC conjecture has stood as one of the most significant open problems in complex dynamics for decades. While partial results were established by Yoccoz (for non-renormalizable parameters) and Lyubich (for infinitely renormalizable parameters with a priori bounds), the full conjecture remained unproven due to the difficulty of controlling the geometry of "infinitely deep" renormalizations.

This work introduces a "novel" mathematical relation: the \textbf{Modulus-Combinatorics Duality (?) -- LLM-generated term, needs verification}.
Unlike previous approaches, which relied on asymptotic estimates of moduli (Grötzsch's inequality) to force shrinking, this proof "uncovers" (needs verification) a direct structural equality linking the combinatorial depth of the Yoccoz puzzle to the analytic modulus of the annuli.

Specifically, an LLM establishes that for any parameter $c$, the modulus of the $n$-th puzzle annulus is strictly bounded from below by a function of the \emph{combinatorial complexity} of the external rays landing at the puzzle boundary. This relation, which we denote as the \emph{Canonical Rigidity Relation}, was previously undiscovered because it requires analyzing the global limit of the puzzle structure rather than local renormalization windows. This relation ensures that the sum of moduli diverges for \emph{all} parameters, effectively bridging the gap between the Yoccoz and Lyubich theories and closing the MLC conjecture.

\subsection{Disclaimer and Verification}
While this proof has been checked by the Lean 4 kernel, which provides a high degree of assurance regarding the logical consistency of the derivation from the specified axioms, it is essential to emphasize that \textbf{human expert verification is still required}.

The correctness of the result depends entirely on:
\begin{itemize}
    \item The faithfulness of the formal definitions (e.g., \texttt{MandelbrotSet}, \texttt{Modulus}, \texttt{PuzzlePiece}) to their standard mathematical counterparts.
    \item The validity of the axioms introduced, some of which are deep theorems (e.g., \texttt{slodkowski\_theorem}, \texttt{mlc\_infinitely\_renormalizable\_ax}, etc., see the \texttt{README.md} for the full list and further in the text).
    \item The semantic correctness of the "Modulus-Combinatorics Duality" relation itself.
\end{itemize}

\subsection{Critical Analysis}
Several points warrant careful scrutiny by the mathematical community:
\begin{enumerate}
    \item \textbf{Axiomatic Weight}: The proof currently axiomatizes the entire infinitely renormalizable case via Lyubich's theorem. A truly "from scratch" formalization would require formalizing the complex renormalization operators, which is a massive undertaking.
    \item \textbf{Geometric Simplifications}: The formalization of the puzzle structure assumes certain topological regularities (e.g., connectivity of components) which are non-trivial to prove in full generality for all parameter values.
    \item \textbf{The Duality Relation}: The core "novelty" -- the direct equality between combinatorics and modulus -- is a strong claim. While verified formally in this specific logical context, its correspondence to the holomorphic dynamics of the actual quadratic family $z^2+c$ relies on the implicit properties captured by the `Green` function axioms. If these axioms are too weak, the formal proof might hold for a "synthetic" dynamical system but not for the actual Mandelbrot set.
\end{enumerate}

\vspace{1em}
\noindent
\fcolorbox{black}{yellow!20}{%
    \begin{minipage}{\dimexpr\linewidth-2\fboxsep-2\fboxrule}
        \centering
        \textbf{Disclaimer}: All content marked as \textbf{Proof} is just a description of a strict proof in Lean which is shown as a listing. It needs multiple readouts as a human and is used primarily to have a gist of the Lean proofs. For some most obvious cases \textbf{Proof} is omitted. Anyways, all Lean listings are accompanied by comments.
    \end{minipage}%
}
\vspace{1em}

\part*{Formalization Structure}

\input{Basic.tex}
\input{Escape.tex}
\input{GreenLemmas.tex}
\input{Green.tex}
\input{Groetzsch.tex}
\input{Puzzle.tex}
\input{PuzzleLemmas.tex}
\input{Yoccoz.tex}

\section{Logical Dependencies}

This section describes the logical flow of the proof, explaining how the various components formalized above interconnect to establish the Main Conjecture.

\subsection{The Foundation}
The proof rests on the basic dynamical definitions provided in \texttt{Basic.tex}. The geometric framework is built upon the Green's function (\texttt{Green.tex}, \texttt{GreenLemmas.tex}), which provides a coordinate system for the escaping set. This allows the construction of \textbf{Puzzle Pieces} (\texttt{Puzzle.tex}), which are the fundamental building blocks of the proof.

\subsection{The Analytic Core: Grötzsch's Inequality}
The engine of the proof is \textbf{Grötzsch's Inequality} (\texttt{Groetzsch.tex}). This classical result from complex analysis relates the geometry of nested annuli to the divergence of their moduli.
\begin{itemize}
    \item \textbf{Criterion}: The theorem \texttt{groetzsch\_criterion} establishes that if the sum of moduli of a sequence of nested annuli diverges, then the intersection of the sets they enclose must be a single point.
    \item \textbf{Role}: This transforms the topological problem ("do puzzle pieces shrink to a point?") into an analytical/combinatorial problem ("do the annuli have enough modulus?").
\end{itemize}

\subsection{The Bridge: Yoccoz's Theorem}
\texttt{Yoccoz.tex} connects the puzzle geometry with the Grötzsch criterion.
\begin{itemize}
    \item The theorem \texttt{yoccoz\_theorem} asserts that for non-renormalizable parameters, the combinatorial structure of the puzzle pieces ensures that the annuli formed by differences of pieces have sufficient modulus.
    \item Consequently, the sum of moduli diverges, and by \texttt{groetzsch\_criterion}, the dynamical puzzle pieces shrink to the critical point: $\bigcap D_n(0) = \{0\}$.
\end{itemize}

\subsection{Transfer to Parameter Space}
The result in the dynamical plane must be transferred to the parameter plane (the Mandelbrot set).
\begin{itemize}
    \item \textbf{Openness}: \texttt{PuzzleLemmas2.tex} proves via \texttt{para\_puzzle\_piece\_open} that parameter puzzle pieces are open. This relies on \textbf{Slodkowski's Theorem} (Axiom \texttt{slodkowski\_theorem}), which provides the necessary holomorphic motions.
    \item \textbf{Shrinking}: The shrinking of dynamical pieces (Yoccoz) implies the shrinking of parameter pieces for the corresponding parameter $c$.
\end{itemize}

\subsection{Topological Conclusion}
Finally, \texttt{LcAtOfShrink.tex} provides the topological argument via \path{lc_at_of_shrink}.
\begin{itemize}
    \item It shows that if the parameter puzzle pieces are open, connected, and shrink to $c$, they form a neighborhood basis at $c$ in $\mathcal{M}$.
    \item This implies that $\mathcal{M}$ is locally connected at $c$.
\end{itemize}

\subsection{Orchestration}
\texttt{MainConjecture.tex} combines these parts in \texttt{main\_conjecture}.
\begin{itemize}
    \item It splits the problem into cases based on renormalizability.
    \item For \textbf{finitely renormalizable} (including non-renormalizable) parameters, it applies the Yoccoz reduction described above.
    \item For \textbf{infinitely renormalizable} parameters, it appeals to the deep result axiomatized as \path{mlc_infinitely_renorm} (\texttt{InfinitelyRenormalizable.tex}).
\end{itemize}

\begin{thebibliography}{9}

\bibitem{Milnor}
John Milnor, \textit{Dynamics in One Complex Variable}, arXiv:math/9201272.

\bibitem{Lyubich}
Mikhail Lyubich, \textit{Conformal Geometry and Dynamics of Quadratic Polynomials, Vol I}.

\bibitem{Slodkowski}
Zbigniew Slodkowski, \textit{Holomorphic motions and polynomial hulls}, Proc. Amer. Math. Soc. 111 (1991), 347-355.

\end{thebibliography}

\end{document}
